\( \tool \): JavaScript IR-based Semantics Extraction Toolchain

### 2020-04-21 ase20/intro.tex
[ASE] slightly revised intro.tex

Our contribution is \( \tool \), a JavaScript IR-based Semantics Extraction
Toolchain:
\begin{itemize}[leftmargin=0.5cm]
  \item \textbf{\( \tool \) is the \textit{first tool that automatically
    extract} IR-based semantics from a language specification, ECMAScript.}
    For syntax, we formally introduce a variant of EBNF, \( \bnfes \),
    and propose a parser generation technique with
    lookahead parsing for \( \bnfes \), which supports automatic semicolon
    insertion. For semantics, we propose semi-automatic synthesis of AST-IR
    translators assisted by compile rules.  Compile rules describe
    how to convert each step of abstract algorithms into our intermediate
    representation \( \ires \) designed for ECMAScript. We evaluated \( \tool \)
    with the four most recent ECMAScript versions (ES7 to ES10).   \( \tool \)
    automatically generated parsers for all versions, and automatically compiled
    \inred{XX.X}\% of the steps in abstract algorithms on average.
  \item \textbf{\( \tool \) bridges the gap between tests and the specification
    written in a natural language.}
    The formal semantics automatically extracted by \( \tool \) is executable
    and its components have one-to-one correspondences with the components of
    the ECMAScript.  It gives opportunity to directly verify the specification
    through the official test conformance suite, Test262~\cite{test262}.  We
    manually completed the missing parts for the latest ECMAScript (ES10, 2019),
    and it is the \textit{first IR-based formal semantics of modern JavaScript}.
    By executing tests, we found \inred{X} specification errors in ES10 and
    \inred{XX} wrong tests in Test262. They were all confirmed by TC39 and will
    be fixed in the next release.  After fixing them, our formal semantics
    passed all \inred{XX,XXX} applicable tests.
  \item \textbf{\( \tool \) is also \textit{forward compatible} with new
    language features proposed for future ECMAScript specifications.}
    We evaluated the forward compatibility of \( \tool \) by applying it to all
    \inred{X} proposals that are ready for inclusion in the next ECMAScript
    (ES11, 2020).  It automatically synthesized parsers and compiled \inred{XXX}
    out of \inred{XXX} algorithm steps for all the proposals.  After completion
    of the missing parts, we found \inred{X} specifications errors by executing
    the corresponding tests in Test262.  After fixing them, the extracted
    semantics passed all \inred{XXX} tests.
\end{itemize}

>>>>

Our contribution is \( \tool \), a JavaScript IR-based Semantics Extraction
Toolchain:
\begin{itemize}[leftmargin=0.5cm]
  \item \textbf{\( \tool \) is the \textit{first tool that automatically
    extract} IR-based semantics from a language specification, ECMAScript.}
    For syntax, we formally introduce a variant of EBNF, \( \bnfes \),
    and propose a parser generation technique with
    lookahead parsing for \( \bnfes \), which supports automatic semicolon
    insertion. For semantics, we propose semi-automatic synthesis of AST-IR
    translators assisted by compile rules.  Compile rules describe
    how to convert each step of abstract algorithms into our intermediate
    representation \( \ires \) designed for ECMAScript. We evaluated \( \tool \)
    with the four most recent ECMAScript versions (ES7 to ES10).   \( \tool \)
    automatically generated parsers for all versions, and automatically compiled
    \inred{XX.X}\% of the steps in abstract algorithms on average.
  \item \textbf{\( \tool \) bridges the gap between tests and the specification
    written in a natural language.}
    The formal semantics automatically extracted by \( \tool \) is executable
    and its components have one-to-one correspondences with the components of
    the ECMAScript.  It gives opportunity to directly check the specification
    through the official test conformance suite, Test262~\cite{test262}.  We
    manually completed the missing parts of the AST-IR translator for the latest
    ECMAScript (ES10, 2019), and it is the \textit{first IR-based formal
    semantics of modern JavaScript}.  By executing tests, we found \inred{X}
    specification errors in ES10 and \inred{XX} wrong tests in Test262. They
    were all confirmed by TC39 and will be fixed in the next release.  After
    fixing them, our formal semantics passed all \inred{XX,XXX} applicable
    tests.
  \item \textbf{\( \tool \) is also \textit{forward compatible} with new
    language features proposed for future ECMAScript specifications.}
    We evaluated the forward compatibility of \( \tool \) by applying it to all
    \inred{X} proposals that are ready for inclusion in the next ECMAScript
    (ES11, 2020).  It automatically synthesized parsers and compiled \inred{XXX}
    out of \inred{XXX} algorithm steps for all the proposals.  After completion
    of the missing parts, we found \inred{X} specifications errors by executing
    the corresponding tests in Test262.  After fixing them, the extracted
    semantics passed all \inred{XXX} tests.
\end{itemize}
